How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-04 tse-paper/content.tex
Ran reindent
Review

\subsection{Choice of Chunk Retrieval Techniques}

@@

\subsection{Keyword Search (KWS)}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad hoc approach they
use is to search for related keywords.
%% TODO Caro: I took this out as it interrupts reading flow. Do you
%% agree?
%% Indeed, this was one of the
%% most common approaches we took when searching for the reason a build
%% failed while creating the \emph{LogChunks} data
%% set~\cite{brandt2020logchunks}.
To investigate the performance of this approach, we designed a chunk
retrieval technique mimcing this human behavior based on keyword
search.

@@

\begin{simplebox}[minipage boxed title*=-1.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} How do build log analysis techniques compare?}
\begin{itemize}[leftmargin=1.2cm]
  \item[\textbf{RQ2.1:}] How many examples does a technique need to
  perform best?
  \item[\textbf{RQ2.2:}] How structurally similar do the examples
  need for a technique to be applicable?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

In the following, we first introduce the data set we created for this
study, and then describe the study design and its
results.

@@

\subsection{Results}
The empirical comparison study yielded diverse results for the
different chunk retrieval techniques
In this section, we first present the results for each chunk retrieval
technique separately.
Afterwards, we compare the three techniques with each other and with a
random baseline.

@@

\section{Discussion}
\label{sec:discussion}

For the interpretation of the study results, we look at each chunk
retrieval technique separately.
Next, we discuss
which criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on the empirical comparison, we present a
decision tree between the three techniques we investigated.

\subsection{Interpretation of Study Results}
Following from the results of the empirical study,
we give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
We summarize these recommendations in
\Cref{tab:single-technique-recommendations}.

@@

\subsection{Recommendation of Suitable Techniques}

\begin{figure}[bt]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/crt-recommendation.pdf}
		\caption{Decision tree for chunk
		retrieval techniques.}
		\label{fig:crt-recommendation}
\end{figure}

We saw that each of the techniques is suited for different types of
log chunks and the output of each is suited for different uses.
Now, we unify these results into conditions to answer
our second research question;
If researchers or developers want to retrieve chunks from build logs,
they can follow these conditions to identify the technique
suited best for their use case.
% I want to ref the figure early bc I believe the text is easier
% to follow when looking at the figure as well
We summarize these conditions in the decision tree in
\Cref{fig:crt-recommendation}.
It is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.
In the next section we give two concrete examples on how to
apply our decision tree.

% we can't just have a paragraph in a scientific paper start with
% Caveat, I think ;-) Also, we should say why we THINK this is not
%the case.
% Otherwise we weaken our work unduly
% Of course we can! xD
% Agree with the rest.
% It's in TtV, quite close actually
% so I'll comment this out
% also #more selling :D
% \textbf{Caveat!}
% This is a preliminary hypothesis based on the results
% from our comparison study.
% The recommendations could therefore be
% influenced by idiosyncrasies of our specific implementation of the
% chunk retrieval techniques as well as the \emph{LogChunks}
% data set.

The first and most important aspect that influences a choice for
a chunk retrieval technique are the structural categories.
In other words:
are the targeted log chunks always presented in
the same structural way within the build logs?
Then the
chunks in all training examples and the analyzed build log are in the
same structural category.
This is why the first question in \Cref{fig:crt-recommendation} asks
how many structural categories the targeted log chunks have.

If the chunks are from multiple structural categories
and recall is more important than precision we recommend
to use KWS\@.
If precision is more important than recall, we
recommend CTS, as \Cref{fig:crt-recommendation} shows on the
right half of the decision tree.
We also recommend CTS when the log chunks are
from one structural category, when the user does not require high
confidence in the precision or recall of the outcome and when one
would rather have output with low recall instead of no output at all.
On the leftmost path of the decision tree,
when the chunks are from one structural category and the user
wishes high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

As a final recommendation, one could create a ``super analyzer'' by
combining the different build log analysis techniques studied in this
paper.
Such a super analyzer would likely always first employ PBE
(because of its high accuracy), followed by a combination of CTS and
KWS\@.
Other than initial setup and training time, there is no
downside to this approach if it is implemented in a transparent way to
the underlying technique: the output of the super analyzer could
include from which sub-technique it originated and thus facilitate
automatic onward processing or interpretation of the result.

\subsection{Exemplary Recommendation}
To illustrate how one would use the decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

@@

In the second example, a researcher wants to investigate whether
small or large groups of test cases
cause CI build failures.
They gather
CI build logs from various projects.
The task of the researcher is to extract the names of the
failing test cases from each build log.
When they use the
decision tree to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researcher is
covering a wide range of test tools, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant chunk---the name of the failing
test case---was not retrieved.
Therefore, following the rightmost path in
\Cref{fig:crt-recommendation},
the decision tree recommends the researcher to use KWS\@.

In case the researcher wants to avoid manually inspecting the
retrieval results, they have to first separate the CI build logs
according to the test tool responsible for logging the test results.
Then the targeted log chunks are from one structural category and they
can use PBE, trained with examples from each test tool separately.

\section{Threats to Validity}
There are several threats to the validity of the conclusions of our
work.

\textbf{Implementation.}
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.
The program synthesis provided by PROSE is the basis for our
implementation of PBE\@.
The
idiosyncrasies of this framework influence the PBE results.
Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.
For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.
PROSE introduced this constraint to
keep the synthesis performance reasonable.
At the same time, this is
clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

The library
{\tt text2vec}~\cite{text2vec2019webpage}
and the way it splits strings into word tokens is influencing
our implementation of CTS\@.
On the other hand,
{\tt text2vec} is the de-facto standard library to do word embeddings
in R.
We intentionally chose a simple, minimally configured or tuned
approach to compare against.
Tuning the text similarity
meta-parameters more to the specific use case of chunk retrieval from
build logs would yield better chunk retrieval results.

% kinda uncreative..
% not sure what another example would be?
% not sure if this adds much on top of the sentences further up
Overall, we believe our implementations and their weaknesses stand
prototypical for the techniques.
We tried to limit idiosyncrasies as much as possible, by choosing
standard approaches and configurations.

\textbf{Data Set.}
The build logs from the \emph{LogChunks} data set highly affect
the outcomes of the comparison study.
\emph{LogChunks} consists of build
logs from open source projects and therefore it is not clear whether
our results apply to industry projects that use build tools
not popular in open source development.
However, since \emph{LogChunks} covers a wide array of build tools and
programming languages,
we believe that the findings do generalize.
We collected build logs from Travis CI.
Yet, the format of the log chunk we chose
for the evaluation is largely independent of Travis CI\@.
This
is because the reason the build failed is described within the build
logs by the tools themselves and not the Travis CI environment.

\textbf{Training Set Size.}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.
We chose this small training set
size as a user has to provide the training examples
per project and one of the central aims of the chunk
retrieval techniques is that they can be set up wit little effort.
The fact that PBE and KWS performed best with already two training
examples shows that the training set size is large enough to
compare the three techniques.

\textbf{Few Samples with Many Structural Categories.}
Our comparison study shows fewer measurements with many structural
categories than with one structural category category (50.25\% one,
33.75\% two, 13.75\% more than two).
This stems from the fact that we
investigated the chunk retrieval techniques on a real-world data set,
where there were mostly few structural categories within one project.
In addition, the third of the measurements we conducted with two
structural categories already showed the negative effect of an
increasing number of structural categories on the performance of the
chunk retrieval techniques.

\section{Future Work}
% Actually, this future work is very, *very* good.
%It might be
% the best future work I have ever read in an article.
% One idea would be to sell it as such and tie a bit back to our
% first literature survey.
%You can say you give a roadmap to guide
% future research in the field, and sell it in abstract and intro!

There are various future research opportunities based on the
work we presented:

\textbf{Systematic Survey of Industry Approaches for Build
Log Analysis.}
Our survey is limited to academic work and articles.
However, handling build logs is a challenge for a wide range of
practitioners as well.
We propose to investigate the techniques used in industry to analyze
build logs.
An example is the Jenkins \emph{build-failure-analyzer}
plugin~\cite{jenkins2020failure-analyzer} or automatically
inferred test results in Azure~\cite{azure2020inferred}.

\textbf{Further Analysis of \emph{LogChunks}.}
We created the
\emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
the comparative
study in this paper, though it can be the basis for various further
analyses of build log data.
The keywords, for example, can be
investigated to answer which keywords are used to search for the
reason the build failed within build logs.

@@

\textbf{Comparison with more Chunk Retrieval Techniques.}
This
paper investigates the three chunk retrieval techniques PBE, CTS, and
KWS\@.
Our study design can be reused to evaluate other build log
analysis techniques, such as the parser Tomassi et al.
used to create
BugSwarm~\cite{tomassi2019bugswarm} or the regex-based approach
Beller et al.
used to create TravisTorrent~\cite{beller2017oops}.

\textbf{Refinement of Retrieval Quality for each Technique.} We
investigated basic configurations of existing techniques applied to
chunk retrieval from build logs.
In a next step, each of these
techniques could be refined to better approach the domain of build
logs.
The \emph{LogChunks} data set and our study results act as a
baseline to benchmark such technique improvements.
We propose the
following improvements:
\begin{itemize}[leftmargin=0.4cm]
  \item \textbf{Custom Ranking and Tokens for PBE.} The program
  synthesis through PROSE ranks possible programs according to
  what the user most likely intended.
  One could adapt the ranking
  rules provided by the FlashExtract DSL to fit common build log
  chunk retrieval tasks.
  FlashExtract includes special tokens when
  enumerating possible regular expressions.
  One could extend these
  with tokens found in build logs, such as ``-,''
	``=,'' ``ERROR,''
  or ``[OK]''.
  \item \textbf{Meta-Parameter Optimization for CTS.} Information
  retrieval techniques have various meta-parameters which can be
  optimized for the specific use
  case~\cite{panichella2016parameterizing}.
  We propose to further
  investigate improvements in preprocessing of the log text, in
  tokenization of the log lines into terms and in stop words
  lists.
\end{itemize}

@@

The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.
To this end, we
conducted a systematic mapping survey to map out the available build
log analysis techniques.
We saw that, while build log analysis is widely used, it is often
a side part of a work and implementations are rarely reused.
This shows the need for a new generation of generic and automated
build log analysis techniques that need little effort to set up.

@@

We evaluated the performance of these chunk retrieval techniques on the
\emph{LogChunks} data set and saw varying results.
CTS had the highest average F$_{1}$-score with 51\%, while the other
techniques showed higher average scores for precision (95\%, PBE)
and recall (70\%, KWS).

To guide researchers and developers on which technique suits their
use case,
we summarized our results in a decision tree.
We found
that the structural representation of the targeted information in the
build logs is the main factor a user should consider when they
choose a
technique.
Secondary factors are the desired confidence in recall and
precision of the produced output and whether precision or recall is
more important for the task at hand.

Finally, we gave an
outline to guide future research efforts in the area of build log
analysis.
Important themes are a systematic investigation of industry approaches,
benchmarks of existing build log analysis approaches and further
refinement of the chunk retrieval techniques we proposed.
We strongly believe that further research into the techniques to
analyze build logs will support researchers and developers alike to
leverage the vast amounts of valuable information
hidden within build logs.

>>>>

\subsection{Choice of Chunk Retrieval Techniques}
\label{sec:choice}

@@

\subsection{Keyword Search (KWS)}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad hoc approach they
use is to search for related keywords.
%% TODO Caro: I took this out as it interrupts reading flow.
%% Do you
%% agree?
%% Indeed, this was one of the
%% most common approaches we took when searching for the reason a build
%% failed while creating the \emph{LogChunks} data
%% set~\cite{brandt2020logchunks}.
To investigate the performance of this approach, we designed a chunk
retrieval technique mimcing this human behavior based on keyword
search.

@@

\begin{simplebox}[minipage boxed title*=-1.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} How do build log analysis techniques compare?}
\begin{itemize}[leftmargin=1.2cm]
  \item[\textbf{RQ2.1:}] With how many examples does a technique perform best?
  \item[\textbf{RQ2.2:}] How structurally variable can configuration examples be?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

In the following, we first introduce the data set we created for this
study, and then describe the study design and its
results. We answer these RQs separately for each technique.

@@

\subsection{Results}
In this section, we first present the results for each chunk retrieval
technique separately.
Afterwards, we compare the three techniques with each other and with a
random baseline.

@@

\subsection{Discussion}
\label{sec:discussion}

Following from the results of the empirical study, in this section,
we give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
We summarize these recommendations in
\Cref{tab:single-technique-recommendations}.

@@

\subsection{Usage Recommendation}
In this section, we derive a decision tree to help practitioners and
researchers choose a suitable chunk retrieval technique. We then
illustrate its use on two examples.

\subsubsection{Derivation of Decision Tree}
\begin{figure}[bt]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/crt-recommendation.pdf}
		\caption{Decision tree for chunk
		retrieval techniques.}
		\label{fig:crt-recommendation}
\end{figure}

Abstractly, we have learned that every chunk retrieval technique
differs in its suitability depending on the kinds of logs it should
operate on and the sort of output one expects.  In this section, we
unify these findings, culminating in the creation of a decision tree
to help developers and researchers choose an adequate technique in
\Cref{fig:crt-recommendation}.

The first and most important aspect that influences the decision for a
chunk retrieval technique is the presence of different structural
categories in the log (or lack therefore).  Are the targeted log
chunks always present in the same structural way within the build logs
(first question in \Cref{fig:crt-recommendation})?  If so, the chunks
in all training examples and the analyzed build log are in the same
structural category
%TODO ... and what? PBE is the best technique?
If the chunks are from multiple structural categories and recall is
more important than precision, we recommend to use KWS\@.
% TODO because ?

If precision is more important than recall, we
recommend CTS, as \Cref{fig:crt-recommendation} shows on the
right half of the decision tree.
We also recommend CTS when the log chunks are
from one structural category, when the user does not require high
confidence in the precision or recall of the outcome, and when one
would rather have output with low recall instead of no output at all.
On the leftmost path of the decision tree,
when the chunks are from one structural category and the user
needs high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

As a final recommendation, one could create a ``super analyzer'' by
combining the different build log analysis techniques studied in this
paper.  Such a super analyzer would likely always first employ PBE
(because of its high accuracy), followed by a combination of CTS and
KWS\@.  Other than initial setup and training time, there is no
downside to this approach if it is implemented in a transparent way:
the output of the super analyzer could include from which
sub-technique it originated and thus facilitate automatic onward
processing or interpretation of the result.

\subsubsection{Example Use Cases}
To illustrate how one would use the decision tree to find a suitable
chunk retrieval technique we describe here two concrete examples: a software
team
wanting to monitor their build performance and a
group of researchers investigating why builds fail.

@@

In the second example, a researcher wants to investigate whether
small or large groups of test cases
cause CI failures.
They gather
CI build logs from various projects.
Their aim is to extract the names of the
failing test cases from the build logs.
When they use the
decision tree to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researchers are
covering a wide range of test tools, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant chunk---the name of the failing
test case---was not retrieved.
Therefore, following the rightmost path in
\Cref{fig:crt-recommendation},
the decision tree recommends the researcher to use KWS\@.  An
alternate, potentially more laborious but also more precise solution
could be for researchers to first separate the CI build logs by the
test tool responsible for logging the test results.  Then, the
targeted log chunks are from one structural category and they can use
PBE, trained with examples from each test tool separately.

\section{Threats to Validity}
In this section, we outline threats to the validity of our work and
show how we mitigated them.

% TODO Caro: fill in the maven analyzer plugin and others.
\textbf{Limitation to Scholarly Articles.} We limited our literature survey to scholarly articles. However, the field of build log analysis is extremely relevant to practitioners, too. While it is difficult to systematically sight all such non-scientific material, we ran several Google search queries related to build log analysis and evaluted them informally. Our findings include the Jenkins build log analyzer and a web page on which Microsoft details how its CI service, Azure Pipes, uses a PBE-approach for certain log formats such as Python. This inspired the choice of PBE in \Cref{sec:choice}.

\textbf{Implementation.}
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.

The program synthesis
provided by PROSE is the basis for our implementation of PBE\@.  The
idiosyncrasies of this framework influence the PBE results.  Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.  For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.  PROSE introduced this constraint
to keep the synthesis performance reasonable.  At the same time, this
is clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

Similarly, the library
{\tt text2vec}~\cite{text2vec2019webpage}
and the way it splits strings into word tokens is influencing
our implementation of CTS\@.
On the other hand,
{\tt text2vec} is the de-facto standard library to do word embeddings
in R.
We intentionally chose a simple, minimally configured or tuned
approach to compare against.
Tuning the text similarity
meta-parameters more to the specific use case of chunk retrieval from
build logs would yield better chunk retrieval results.

% TODO (resolved)
% kinda uncreative..
% not sure what another example would be?
% not sure if this adds much on top of the sentences further up
%% Yup, it's super cool and I expanded it a bit
Overall, we believe our implementations and their weaknesses stand
prototypical for the techniques.  We tried to limit idiosyncrasies as
much as possible, by choosing standard approaches and minimizing
configuration, instead of parameterizing and fine-tuning methods
specific to our data set.

\textbf{Data Set.}
Just like the implementations, the specific build logs from the \emph{LogChunks} data set affect
the outcomes of the comparison study.
\emph{LogChunks} consists of build
logs from open source projects and therefore it is unclear to which
degree our results apply to industry projects that use build tools not
popular in open source development.  However, since \emph{LogChunks}
covers a wide array of build tools and programming languages, we
believe that the findings do generalize. In addition, build log output
of such a tool would need to be wildly different from how the over 27
tools covered in our study do it---this seems unlikely.

We collected build logs from
Travis CI.  Yet, the format of the log chunk we chose for the
evaluation is largely independent of Travis CI\@, because the reason
the build failed is described within the build logs by the tools
themselves and not the Travis CI environment.

\textbf{Training Set Size.}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.  We chose this small training
set size as a human has to provide the training examples and one of
the central aims of the chunk retrieval techniques is that they can be
set up wit little effort.  The fact that KWS and CTS performed best
with already two training examples indicates that the maximum training
set size of five is sufficiently large for research evaluation.

\textbf{Few Samples with Many Structural Categories.}
Our comparison study includes fewer measurements with many structural
categories than with one structural category category (50.25\% one,
% TODO This does not add up to 1. Please no decimals,
% we do not need so much precision here. Also tell % of what?
33.75\% two, 13.75\% more than two).  This distribution mirrors the
structural categories in a real-world data set, where there were
mostly few structural categories within one project.  In addition, the
third of the measurements we conducted with two structural categories
already showed the negative effect of an increasing number of
structural categories on the performance of the chunk retrieval
techniques.

\section{Future Work}
In this section, we describe what we believe are fruitful future
research directions in the field of build log analysis. We base our
assessment on the results of the literature survey and combine it with
findings from our technique comparsion study.

\textbf{Systematic Survey of Industry Approaches for Build
Log Analysis.}  Our survey is limited to scholarly material.  However,
handling build logs is a challenge for a wide range of practitioners
as well.  We propose to investigate the techniques used in industry to
analyze build logs.  An example is the
Jenkins \emph{build-failure-analyzer}
plugin~\cite{jenkins2020failure-analyzer} or automatically inferred
test results in Azure~\cite{azure2020inferred}. Such a study might
also need to tackle the more abstract problem of how to survey
non-scholarly material systematically, which might be an important
contribution to Software Engineering research.

\textbf{Further Analysis of \emph{LogChunks}.}
We created the
\emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
the comparative
study in this paper, though it can be the basis for various further
analyses of build log data.
% TODO Passive overflow
The keywords, for example, can be
investigated to answer which keywords are used to search for the
reason the build failed within build logs.

@@

\textbf{Comparison with more Chunk Retrieval Techniques.}
In this article, we investigated the three chunk retrieval techniques PBE, CTS, and
KWS\@.
Our study design can be reused to evaluate other build log
analysis techniques, such as the parser Tomassi et al.
used to create
BugSwarm~\cite{tomassi2019bugswarm} or the regex-based approach
Beller et al.
used to create TravisTorrent~\cite{beller2017oops}.

\textbf{Refinement of Retrieval Quality.} We
investigated basic configurations of existing techniques applied to
chunk retrieval from build logs.
In a next step, each of these
techniques could be refined to better customize it to the domain of build
logs.
The \emph{LogChunks} data set and our study results act as a
baseline to benchmark such technique improvements.
We propose the
following improvements:
\begin{itemize}[leftmargin=0.4cm]
  \item \textbf{Custom Ranking and Tokens for PBE.} Program
  synthesis through PROSE ranks possible programs according to
  what the user most likely intended.
  One could adapt the ranking
  rules provided by the FlashExtract DSL to fit common build log
  chunk retrieval tasks.
  FlashExtract includes special tokens when
  enumerating possible regular expressions.
  One could extend these
  with tokens found in build logs, such as ``-,''
	``=,'' ``ERROR,''
  or ``[OK]'' to improve results.
  \item \textbf{Meta-Parameter Optimization for CTS.} Information
  retrieval techniques have various meta-parameters which can be
  optimized for the specific use
  case~\cite{panichella2016parameterizing}.
  We propose to further
  investigate improvements in preprocessing of the log text, in
  tokenization of the log lines into terms, and in stop words
  lists.
\end{itemize}

@@

The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.  To this end, we
conducted a systematic mapping survey to map out the available build
log analysis techniques.  We saw that build log analysis is an
emerging field. At the same time, articles largely do not justify why
they use a certain technique, nor do they document it in detail or
open-sourced its implementation. Moreover, the survey showed that,
while there is a niche for custom parsers and plugins for very popular
tools such as the Java ecosystem, there is a wide variety of build
tool and enviroment combinations for which the creation of such
bespoke tooling is unlikely.  Overall, we showed the need for a new
generation of generic and automated build log analysis techniques that
need little effort to set up, both for practitioners as well as
researchers.

@@

We evaluated the performance of these chunk retrieval techniques on the
\emph{LogChunks} data set and saw varying results.
CTS had the highest average F$_{1}$-score with 51\%, while the other
techniques showed higher average scores for precision (95\%, PBE) and
recall (70\%, KWS). Overall, all technqiues vastly outperformed a
baseline of random line retrieval.

To guide researchers and developers on which technique suits their
use case,
we summarized our results in a decision tree.
We found
that the structural representation of the targeted information in the
build logs is the main factor one should consider when 
choosing a build log analysis
technique.
Secondary factors are the desired confidence in recall and
precision of the produced output and whether precision or recall is
more important for the task at hand.

Finally, we gave an
outline to guide future research efforts in the area of build log
analysis.
Important themes are a systematic investigation of industry approaches,
benchmarks of existing build log analysis approaches, and further
refinement of the chunk retrieval techniques we proposed.
We strongly believe that further research into the techniques to
analyze build logs will support researchers and developers alike to
leverage the vast amounts of valuable information hidden
in build logs.
